Boundary Labeling for annotated documents

### 2018-04-29 LaTeX/Paper.tex
Paper: No changes. Program: Fixed bug in uniform text generation. Added 'longer words' mode. Modified R script to better label the combined histogram/boxplot.

Across every test run, the first two instances always took significantly longer to complete than subsequent ones. As this was replicated even when using the same text for all 100 passes, we believe this to be an issue caused by the implementation rather than the algorithm itself. 
\change{Another issue was a significantly increased execution time for some instances, which could not be reproduced in subsequent tests under the same conditions and are assumed to be caused by differences in scheduling or Java's garbage collection. Disregarding these outliers, the worst time measured across all tests was about two milliseconds.}%Wie kann ich einbauen, dass der Computer heiß läuft?

@@

The effects of clustering are currently minor, and mostly outweighed by the influence of vertical placement, as the average word length is short enough that there is enough whitespace in each line to avoid leaders from blocking each other. Increasing the word length would make this effect more severe, and it would be interesting to see the influence on the results.
%While increasing the standard deviation for the annotation placement process also allowed some texts to reach a better label area usage, the average results became worse for that category, whereas the percentage of successful routings moves closer to the 50\% mark.

>>>>

Across every test run, the first two instances always took significantly longer to complete than subsequent ones. As this was replicated even when using the same text for all 100 passes, we believe this to be an issue caused by the implementation rather than the algorithm itself. 
\change{Another issue was a significantly increased execution time for some instances, which could not be reproduced in subsequent tests under the same conditions and are assumed to be caused by differences in scheduling or Java's garbage collection. Disregarding these outliers, the worst time measured across all tests was about two milliseconds.}%Wie kann ich sagen, dass der Computer heiß läuft?

@@

The effects of clustering are minor, and mostly outweighed by the influence of vertical placement, as the average word length is short enough that there is enough whitespace in each line to avoid leaders from blocking each other.
%Increasing the word length would make this effect more severe, and it would be interesting to see the influence on the results.
